Comparative study of Dask and Spark for neuroimaging pipelines\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Natural Sciences and Engineering Research Council}

### 2019-06-20 latex/paper.tex
Modified results section

\begin{table}[!t]
    \caption{Function time for the sleep experiment}
    \begin{subtable}[b]{\columnwidth}
        \renewcommand{\arraystretch}{1.3}
        \caption{Overhead time in second}\label{tab:inc_sleep_overhead}
        \centering
        \begin{tabular}{lllll}
        \hline
                     & 1 sec. & 4 sec. & 16 sec. & 64 sec. \\ \hline
        Spark        & 14992  & 17076  & 16069   & 9769    \\
        Dask.Bag     & 20690  & 21388  & 17759   & 18720   \\
        Dask.Delayed & 27481  & 26199  & 22080   & 24624   \\
        Dask.Futures & 27069  & 27984  & 23538   & 24762   \\ \hline
        \end{tabular}
    \end{subtable}
    \vskip 0.2cm
    \begin{subtable}[b]{\columnwidth}
        \renewcommand{\arraystretch}{1.3}
        \caption{IO time in second}\label{tab:inc_sleep_io}
        \centering
        \begin{tabular}{lllll}
        \hline
                     & 1 sec. & 4 sec. & 16 sec. & 64 sec. \\ \hline
        Spark        & 63622  & 57144  & 51070   & 57078   \\
        Dask.Bag     & 54630  & 52312  & 53743   & 53612   \\
        Dask.Delayed & 45239  & 44142  & 45133   & 46198   \\
        Dask.Futures & 46537  & 43161  & 44749   & 45846   \\ \hline
        \end{tabular}
    \end{subtable}
 \end{table}

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_sleep.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_sleep}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_sleep.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_sleep}
    \end{subfigure}
    \caption{125 chunks, 10 iterations, 8 instances}
\end{figure}

%% Baseline gantt chart
\subsection{Experimentation 1: Baseline timeline}
From Table~\ref{tab:inc_base} and Figure, the frameworks have
similar makespan however the time spend for each type of task differs significantly.
Spark tends to spend more time than other frameworks for IO however it has a much
lower overhead. Dask Delayed and Futures have the lowest IO time but a much higher
overhead. Dask Bag stands in the middle for both IO and overhead. Compute time is
approximately the same for all frameworks.

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_inc_baseline_gantt.png}
        \caption{Spark execution timeline}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_bag_inc_baseline_gantt.png}%
        \caption{Dask Bag execution timeline}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_delayed_inc_baseline_gantt.png}%
        \caption{Dask Delayed execution timeline}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_futures_inc_baseline_gantt.png}%
        \caption{Dask Futures execution timeline}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{125 chunks, 4 sec.\ sleep delay, 8 instances}
\end{figure*}

\begin{table}[!b]
    \renewcommand{\arraystretch}{1.3}
    \caption{Distribution of the execution time in second: 125 chunks, 4 sec.\ sleep
    delay, 10 iterations, and 8 workers}\label{tab:inc_base}
    \centering
    \begin{tabular*}{\columnwidth}{llllll}
    \hline
                 & Read  & Compute & Write & Overhead & Total \\ \hline
    Spark        & 34465 & 5118    & 22679 & 17076    & 79338 \\
    Dask Bag     & 36863 & 5121    & 15449 & 21388    & 78821 \\
    Dask Delayed & 32769 & 5119    & 11373 & 26199    & 75461 \\
    Dask Futures & 31891 & 5120    & 11270 & 27984    & 76265 \\ \hline
    \end{tabular*}
 \end{table}

>>>>

\begin{table}[!t]
    \caption{Function time for the sleep experiment}
    \begin{subtable}[b]{\columnwidth}
        \renewcommand{\arraystretch}{1.3}
        \caption{Overhead time in second}\label{tab:inc_sleep_overhead}
        \centering
        \begin{tabular}{lllll}
        \hline
                     & 1 sec. & 4 sec. & 16 sec. & 64 sec. \\ \hline
        Spark        & 14992  & 17076  & 16069   & 9769    \\
        Dask.Bag     & 20690  & 21388  & 17759   & 18720   \\
        Dask.Delayed & 27481  & 26199  & 22080   & 24624   \\
        Dask.Futures & 27069  & 27984  & 23538   & 24762   \\ \hline
        \end{tabular}
    \end{subtable}
    \vskip 0.2cm
    \begin{subtable}[b]{\columnwidth}
        \renewcommand{\arraystretch}{1.3}
        \caption{IO time in second}\label{tab:inc_sleep_io}
        \centering
        \begin{tabular}{lllll}
        \hline
                     & 1 sec. & 4 sec. & 16 sec. & 64 sec. \\ \hline
        Spark        & 63622  & 57144  & 51070   & 57078   \\
        Dask.Bag     & 54630  & 52312  & 53743   & 53612   \\
        Dask.Delayed & 45239  & 44142  & 45133   & 46198   \\
        Dask.Futures & 46537  & 43161  & 44749   & 45846   \\ \hline
        \end{tabular}
    \end{subtable}
    \vspace{-3mm}
 \end{table}

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_sleep.png}%
        \caption{Incrementation makespan}\label{fig:inc_ms_sleep}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/inc_idle_sleep.png}%
        \caption{Incrementation total time}\label{fig:inc_tt_sleep}
    \end{subfigure}
    \caption{125 chunks, 10 iterations, 8 instances}
\end{figure}

%% Baseline gantt chart
\subsection{Experimentation 1: Baseline timeline}
Figure\ref{fig:inc_gantt} shows the tasks timeline for each worker thread. On the
x-axis is the time in seconds and on the y-axis is the workers and their threads. The
color represents the type of different tasks; note that the color differs from one
graph to another. The first section of reading tasks is much larger than the
following ones. This is because, initially, the NFS is saturated by the number of
workers accessing it. Also, a substantial amount of overhead happens near the IO
tasks. Moreover, for the computing tasks, there is more overhead for the latter tasks.

% The frameworks have similar makespan however the time spend for each type of
% task differs considerably (see Table~\ref{tab:inc_base}). Spark tends to spend more
% time than other frameworks for IO however it has a much lower overhead. Dask Delayed
% and Futures have the lowest IO time but a much higher overhead. Dask Bag stands in
% the middle for both IO and overhead. Compute time is approximately the same for all
% frameworks. Apart from the first IO section, there is a large amount of ovehead
% everytime time IO is performed. This is true for all frameworks.

\begin{figure*}[!htb]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/spark_inc_baseline_gantt.png}
        \caption{Spark execution timeline}\label{fig:inc_spark_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_bag_inc_baseline_gantt.png}%
        \caption{Dask Bag execution timeline}\label{fig:inc_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_delayed_inc_baseline_gantt.png}%
        \caption{Dask Delayed execution timeline}\label{fig:inc_dask_delayed_gantt}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/Dask_futures_inc_baseline_gantt.png}%
        \caption{Dask Futures execution timeline}\label{fig:inc_dask_futures_gantt}
    \end{subfigure}
    \caption{125 chunks, 4 sec.\ sleep delay, 8 instances}\label{fig:inc_gantt}
\end{figure*}

% \begin{table}[!b]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Distribution of the execution time in second: 125 chunks, 4 sec.\ sleep
%     delay, 10 iterations, and 8 workers}\label{tab:inc_base}
%     \centering
%     \begin{tabular*}{\columnwidth}{llllll}
%     \hline
%                  & Read  & Compute & Write & Overhead & Total \\ \hline
%     Spark        & 34465 & 5118    & 22679 & 17076    & 79338 \\
%     Dask Bag     & 36863 & 5121    & 15449 & 21388    & 78821 \\
%     Dask Delayed & 32769 & 5119    & 11373 & 26199    & 75461 \\
%     Dask Futures & 31891 & 5120    & 11270 & 27984    & 76265 \\ \hline
%     \end{tabular*}
%  \end{table}
